Fine-scale Twitter Big Data Reveals Neighborhood Inequalities in Mental Health Effects of High Temperatures

### 2021-05-18 doc/temp-sentiment.tex

\begin{figure}[H]
\centering
  \includegraphics[width=\linewidth]{../res/wbgt_combined.png}
    \caption{Effect of changes in wet-bulb globe temperature on expressed sentiment relationship as moderated by neighborhood income (A) and race (B).}
\label{fig:hetero}
\end{figure}

@@

\begin{figure}[H]
\centering
  \includegraphics[width=0.5\linewidth]{../res/map_combined.png}
  \caption{}
  \label{fig:map}
\caption{Figure A shows the change in sentiment for a 25-degree increase in WBGT for cities with a population of over 1 million.  Figures B and C show inequalities in impacts of temperature on sentiment for cities with over 1 million people.  The value shown is the predicted change in the size of the gap in VADER score as temperatures increase from 5\textdegree C WBGT to 30\textdegree C WBGT between the 5th and 95 percentile for income (A) and the 95th and 5th percentile for percent black (B).  Cities with a statistically significant effect ($p < 0.05$) are outlined in black.  For racial inequalities (B), only cites where black people make up $> 5\%$ of the population are included.}
\end{figure}

>>>>

\begin{figure}[H]
\centering
  \includegraphics[width=\linewidth]{../res/wbgt_combined.png}
    \caption{Effect of changes in wet-bulb globe temperature on expressed sentiment relationship as moderated by neighborhood income (a) and race (b).}
\label{fig:hetero}
\end{figure}

@@

\begin{figure}[H]
\centering
  \includegraphics[width=0.5\linewidth]{../res/map_combined.png}
  \label{fig:map}
    \caption{Figure (a) shows the change in sentiment for a 25-degree increase in WBGT for cities with a population of over 1 million.  Figures (b) and (c) show inequalities in impacts of temperature on sentiment for cities with over 1 million people.  The value shown is the predicted change in the size of the gap in VADER score as temperatures increase from 5\textdegree C WBGT to 30\textdegree C WBGT between the 5th and 95 percentile for income (a) and the 95th and 5th percentile for percent black (b).  Cities with a statistically significant effect ($p < 0.05$) are outlined in black.  For racial inequalities (b), only cites where black people make up $> 5\%$ of the population are included.}
\end{figure}
